# RStudio Tips, Tricks, and Shortcuts {#ch3_shortcuts}



**Shortcuts in Rstudio**

RStudio provides a variety of keyboard shortcuts that can help R users save time and streamline their workflows.<br>

Here are some of the most common and useful shortcuts for working in the code editor:

**Working on RMarkdown **

* The command to clear all variables from the environment (workspace)
```{r}
rm(list=ls())
```

* To insert an R code chunk in your R Markdown document, press Press **Ctrl + Alt + I** This shortcut can save you time when you want to quickly add new chunks to your document. Once the chunk is inserted, you can add your R code inside the curly braces (**{}**) and specify any chunk options, such as the chunk label, the type of output, and any additional settings.
```{r}
# Insert R code here.
```


**Working on the Code Editor **

* To quickly insert the **<-** symbol, which is used to assign values in R, press **Alt GR + -** on your keyboard.

* To hide the code pane, press **Alt + L**.

* To execute code, use these shortcuts:<br>
  * Press **Ctrl + Enter** to run the current line of code.<br>
  * Press **Ctrl + Alt + R** to run the entire code.

</br>

**Working in _dplyr_**  

dplyr is a powerful R package for data manipulation. 

* To quickly insert the pipe operator into your code, use the following keyboard shortcut, press **Ctrl + Shift + M** to insert **%>%**. This shortcut can save you time and help make your code more readable by breaking up long chains of commands into multiple lines.

</br>
</br>